Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-04 alloscore_manuscript/supplement.rnw
a little more search iteration yoga

>>>>

Iterating this process we obtain a sequence $\{I_k\}, k=1,2,\ldots$ of intervals of widths 
$\left|I_k \right| = 2^{1-k}\left|I_1 \right|$ which either terminates at one of the scenarios 
($\bullet$), ($\bullet\!-$), or ($-\!\bullet$), or provides infinite sequences $\{\tau_{L,k}\}$ and $\{\tau_{U,k}\}$ converging
to $\tau^{\star}$ from below and above.

In the generic case of an infinite $\{I_k\}$, we need to define practical stopping criteria for each of three possible behaviours of 
$F_T$ at $K$:
\begin{samepage}
\begin{itemize}
\item[($\,\mathrlap{\,\bullet}{\diagup}\,$)] $\tau^{\star} = F_T(K-)$ and $TQ_F(\tau^{\star}) = \{K\}$ (that is, if $F_T$ is continuous and strictly increasing at $K$)
\item[(\raisebox{-.5ex}{$-$}\!\!\raisebox{.5ex}{$\bullet\!-$})] $F_T$ has a point mass at $K$
\item[($-\!\!\!\bullet\!\!\!-$)] $K \in (q^{-}_{F_T,\tau^{\star}}, q^{+}_{F_T,\tau^{\star}})$ (that is, all component forecasts $F_i$ have zero density at points $x_i \in (q^{-}_{F_i,\tau^{\star}}, q^{+}_{F_i,\tau^{\star}})$ and $\sum x_i = K$).
\end{itemize}
\end{samepage}
